---
title: "CodeBook"
author: "Ali Asghar"
date: "Saturday, December 20, 2014"
output: html_document
---

Was code book submitted to GitHub that modified and updates the codebooks available to you with the data to indicate all the variables and summaries you calculated, along with units, and any other relevant information?

#Data Dictionary - Samsung Data
##Hello
###Hello
> yes this is a quote

*Hello



```{r}
summary(cars)
```

You can also embed plots, for example:

```{r, echo=FALSE}
plot(cars)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.


\name{tidyDataSet_2}
\alias{tidyDataSet_2}
\docType{data}
\title{
%%   ~~ data name/kind ... ~~
}
\description{
%%  ~~ A concise (1-5 lines) description of the dataset. ~~
}
\usage{data("tidyDataSet_2")}
\format{
  A data frame with 180 observations on the following 68 variables.
  \describe{
    \item{\code{subject}}{a numeric vector}
    \item{\code{activity}}{a character vector}
    \item{\code{tBodyAcc.mean.X}}{a numeric vector}
    \item{\code{tBodyAcc.mean.Y}}{a numeric vector}
    \item{\code{tBodyAcc.mean.Z}}{a numeric vector}
    \item{\code{tGravityAcc.mean.X}}{a numeric vector}
    \item{\code{tGravityAcc.mean.Y}}{a numeric vector}
    \item{\code{tGravityAcc.mean.Z}}{a numeric vector}
    \item{\code{tBodyAccJerk.mean.X}}{a numeric vector}
    \item{\code{tBodyAccJerk.mean.Y}}{a numeric vector}
    \item{\code{tBodyAccJerk.mean.Z}}{a numeric vector}
    \item{\code{tBodyGyro.mean.X}}{a numeric vector}
    \item{\code{tBodyGyro.mean.Y}}{a numeric vector}
    \item{\code{tBodyGyro.mean.Z}}{a numeric vector}
    \item{\code{tBodyGyroJerk.mean.X}}{a numeric vector}
    \item{\code{tBodyGyroJerk.mean.Y}}{a numeric vector}
    \item{\code{tBodyGyroJerk.mean.Z}}{a numeric vector}
    \item{\code{tBodyAccMag.mean}}{a numeric vector}
    \item{\code{tGravityAccMag.mean}}{a numeric vector}
    \item{\code{tBodyAccJerkMag.mean}}{a numeric vector}
    \item{\code{tBodyGyroMag.mean}}{a numeric vector}
    \item{\code{tBodyGyroJerkMag.mean}}{a numeric vector}
    \item{\code{fBodyAcc.mean.X}}{a numeric vector}
    \item{\code{fBodyAcc.mean.Y}}{a numeric vector}
    \item{\code{fBodyAcc.mean.Z}}{a numeric vector}
    \item{\code{fBodyAccJerk.mean.X}}{a numeric vector}
    \item{\code{fBodyAccJerk.mean.Y}}{a numeric vector}
    \item{\code{fBodyAccJerk.mean.Z}}{a numeric vector}
    \item{\code{fBodyGyro.mean.X}}{a numeric vector}
    \item{\code{fBodyGyro.mean.Y}}{a numeric vector}
    \item{\code{fBodyGyro.mean.Z}}{a numeric vector}
    \item{\code{fBodyAccMag.mean}}{a numeric vector}
    \item{\code{fBodyBodyAccJerkMag.mean}}{a numeric vector}
    \item{\code{fBodyBodyGyroMag.mean}}{a numeric vector}
    \item{\code{fBodyBodyGyroJerkMag.mean}}{a numeric vector}
    \item{\code{tBodyAcc.std.X}}{a numeric vector}
    \item{\code{tBodyAcc.std.Y}}{a numeric vector}
    \item{\code{tBodyAcc.std.Z}}{a numeric vector}
    \item{\code{tGravityAcc.std.X}}{a numeric vector}
    \item{\code{tGravityAcc.std.Y}}{a numeric vector}
    \item{\code{tGravityAcc.std.Z}}{a numeric vector}
    \item{\code{tBodyAccJerk.std.X}}{a numeric vector}
    \item{\code{tBodyAccJerk.std.Y}}{a numeric vector}
    \item{\code{tBodyAccJerk.std.Z}}{a numeric vector}
    \item{\code{tBodyGyro.std.X}}{a numeric vector}
    \item{\code{tBodyGyro.std.Y}}{a numeric vector}
    \item{\code{tBodyGyro.std.Z}}{a numeric vector}
    \item{\code{tBodyGyroJerk.std.X}}{a numeric vector}
    \item{\code{tBodyGyroJerk.std.Y}}{a numeric vector}
    \item{\code{tBodyGyroJerk.std.Z}}{a numeric vector}
    \item{\code{tBodyAccMag.std}}{a numeric vector}
    \item{\code{tGravityAccMag.std}}{a numeric vector}
    \item{\code{tBodyAccJerkMag.std}}{a numeric vector}
    \item{\code{tBodyGyroMag.std}}{a numeric vector}
    \item{\code{tBodyGyroJerkMag.std}}{a numeric vector}
    \item{\code{fBodyAcc.std.X}}{a numeric vector}
    \item{\code{fBodyAcc.std.Y}}{a numeric vector}
    \item{\code{fBodyAcc.std.Z}}{a numeric vector}
    \item{\code{fBodyAccJerk.std.X}}{a numeric vector}
    \item{\code{fBodyAccJerk.std.Y}}{a numeric vector}
    \item{\code{fBodyAccJerk.std.Z}}{a numeric vector}
    \item{\code{fBodyGyro.std.X}}{a numeric vector}
    \item{\code{fBodyGyro.std.Y}}{a numeric vector}
    \item{\code{fBodyGyro.std.Z}}{a numeric vector}
    \item{\code{fBodyAccMag.std}}{a numeric vector}
    \item{\code{fBodyBodyAccJerkMag.std}}{a numeric vector}
    \item{\code{fBodyBodyGyroMag.std}}{a numeric vector}
    \item{\code{fBodyBodyGyroJerkMag.std}}{a numeric vector}
  }
}
\details{
%%  ~~ If necessary, more details than the __description__ above ~~
}
\source{
%%  ~~ reference to a publication or URL from which the data were obtained ~~
}
\references{
%%  ~~ possibly secondary sources and usages ~~
}
\examples{
data(tidyDataSet_2)
## maybe str(tidyDataSet_2) ; plot(tidyDataSet_2) ...
}
\keyword{datasets}

