---
title: "ReadMe"
author: "Ali Asghar"
date: "Saturday, December 20, 2014"
output: html_document
---

I was able to follow the README in the directory that explained what the analysis files did. 

#Getting and Cleaning Data Course Project

This repository contains the work that has been done to clean and tidy-up data for the Coursera 'Getting and Cleaning Data' Course.

The work can be split into three parts: 
- Downloading and Loading Data
- Merging, Cleaning and Manipulating Data
- Writing data to output file

##Downloading and Loading Data
The data that was used in this Course was obtained from: (http://archive.ics.uci.edu/ml/datasets/Human+Activity+Recognition+Using+Smartphones). 
The Data was downloaded using this link: (https://d396qusza40orc.cloudfront.net/getdata%2Fprojectfiles%2FUCI%20HAR%20Dataset.zip). 

A directory `G&CD_Dir` is created if it does not already exist and the data is downloaded in it. `unzip` function is used to unzip the files in the same directory. x_test, x_train, y_test, y_train, subject_test, subject_train and features files are loaded from their respective folders using the `read.table` function. 



Include downloading original Data and saving it in the working file

Include the code for reading the file in the ReadMe: 
data <- read.table(file_path, header = TRUE) 
"reference thread on Forum" : https://class.coursera.org/getdata-016/forum/thread?thread_id=50


```{r}
summary(cars)
```

You can also embed plots, for example:

```{r, echo=FALSE}
plot(cars)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
