

#Getting and Cleaning Data Course Project

This repository contains the work that has been done to clean and tidy-up data for the Coursera 'Getting and Cleaning Data' Course.

This Repository has the following files: 
- run_analysis.R: contains the code to download, manipulate and write a tidy dataset to a text file
- CodeBook.md: Contains information on the variables in this repository
- tidyData.txt: Final tidy data created from step 5 of the Course Project Instructions. 

The files are described below in detail: 
## run_analysis.R
 
The work can be split into three parts: 
- Downloading and Loading Data
- Merging, Cleaning and Manipulating Data
- Writing data to output file

###Downloading and Loading Data
The data that was used in this Course was obtained from: (http://archive.ics.uci.edu/ml/datasets/Human+Activity+Recognition+Using+Smartphones). 
The Data was downloaded using this link: (https://d396qusza40orc.cloudfront.net/getdata%2Fprojectfiles%2FUCI%20HAR%20Dataset.zip). 

A directory `G&CD_Dir` is created if it does not already exist and the data is downloaded in it. `unzip` function is used to unzip the files in the same directory. x_test, x_train, y_test, y_train, subject_test, subject_train and features files are loaded from their respective folders using the `read.table` function. 

The orginal x_test and x_train data consists of 561 variables. These 561 variables are named in the `features` data. The subject_test and subject_train data subject number that which each row of x_test and x_train data corresponds to. y_test and y_train data consists of the activity being performed by each subject. 

###Merging, Cleaning and Manipulating Data

First, the `dplyr` package was loaded (assuming that the user already has the package installed.). `dplyr` package is then used to merge, clean and manipulate the data. All the loaded dataframe are converted to `tbl_df` format for easier data manipulation and viewing. 

`rbind_list` function from the `dplyr` package is used to merge x_test with x_train, y_test with y_train and subject_test with subject_train. 

Then, descriptive names were given to variables in the `merged_XData` and `merged_YData` dataframes.

Next `grepl` function is used to select columns that only contain `mean()` or `std()` values. `select` function is then used to eliminate columns with `meanFreq` values.

Subsequently, values in `activity` column in `merged_YData` were given descriptive names that corresponded to the each number. 

`1 WALKING, 2 = WALKING_UPSTAIRS, 3 = WALKING_DOWNSTAIRS, 4 = SITTING, 5 = STANDING, 6 = LAYING`

Next, `merged_SubjectData`, `merged_YData` and `merged_XData` were all merged using `cbind` function to a new dataset called `tidyDataSet_1`. 

To get a independent tidy data set with the average of each variable for each activity and each subject, the `tidyDataSet_1` was first grouped by `subject` and then by `activity` using the `group_by` funtion in the `dplyr` package. Then the `summarise` function was used to generate a new dataframe named `tidyDataSet_2` where the mean of each variable for each activity and each subject was given. The head of the resulting dataset is give below: 

```{r}
> head(tidyDataSet_2)
Source: local data frame [6 x 68]
Groups: subject

  subject           activity tBodyAcc.mean.X tBodyAcc.mean.Y tBodyAcc.mean.Z
1       1             LAYING       0.2215982    -0.040513953      -0.1132036
2       1            SITTING       0.2612376    -0.001308288      -0.1045442
3       1           STANDING       0.2789176    -0.016137590      -0.1106018
4       1            WALKING       0.2773308    -0.017383819      -0.1111481
5       1 WALKING_DOWNSTAIRS       0.2891883    -0.009918505      -0.1075662
6       1   WALKING_UPSTAIRS       0.2554617    -0.023953149      -0.0973020
```


###Writing Output Data

After Merging, Cleaning and Manipulating the data, I end up with the tidy data that was required by the assignment. This data is lastly written to a text file for submission. The code used to write the data to a text file in a new output directory folder is given below: 

```{r}
if(!file.exists(output)) { dir.create(output) }
write.csv(tidyDataSet_2, "./output/tidyData.txt")
```


This text file can then be read by using this command (this code is used from the forum discussions and thus the thread is cited (https://class.coursera.org/getdata-016/forum/thread?thread_id=50): 

```{r}
data <- read.table("./output/tidyData.txt", header = TRUE, sep = ",")
```

explain everything in the repository. 


## CodeBook.md 

CodeBook.md contains information about all the variables in this repository.

## tidyData.txt

This text file contains the final tidy data created from step 5 of the Course Project Instructions.This file was created as a result of writing data in the run_analysis.R file. 